SPARQL on the Open, Decentralised Web

### 2016-07-25 dissertation/conclusions.tex
remove a too bombastic statement

Clearly, Problem~\ref{prob:lawsfuture} is a very interesting one, with
important implications for evaluation, but also because it shifts the
focus of our attention. In this work, the methodology used to study
Problem~\ref{prob:sanity} could be used to gain such understanding,
but at present, the field is too immature to attempt the formulation
of any laws. As noted in Section~\ref{sec:history}, this study is
partly motivated by my subjective experience of why the Web was so
successful. Clearly, this should be studied more objectively, but I am
not aware of any such study. Such study could also be applied to see
if the experiences from the emergence of the Web can be applied to
accelerating the Semantic Web, like I subjectively propose.

>>>>

Clearly, Problem~\ref{prob:lawsfuture} is a very interesting one, with
important implications for evaluation, but also because it shifts the
focus of our attention. In this work, the methodology used to study
Problem~\ref{prob:sanity} could be used to gain such understanding. As
noted in Section~\ref{sec:history}, this study is partly motivated by
my subjective experience of why the Web was so successful. Clearly,
this should be studied more objectively, but I am not aware of any
such study. Such study could also be applied to see if the experiences
from the emergence of the Web can be applied to accelerating the
Semantic Web, like I subjectively propose.
